PK object batch mode trial

### 2023-10-10 data-raw/batchMode_trial_gpm.Rmd
Updating vignette to increase detail to readers.

```{r Evaluating_Choices}
# Evaluation
# Current: my_pk_111p

@@

  return(full_list)
}
gc()

@@

@@

readxl::excel_sheets(paste(Sys.getenv("OD_DIR"),
                           "DataSummary_9_21_2023.xlsx",
                           sep = "/")) # Predictions Evaluation

@@

Dose-normalization and a hierarchical model were the options that produced the least
amount of error in predictions and derived TK stats.
In addition, _L-GFGS-B_ was the optimizer of choice

@@

@@

The purpose of the following code is to generate data.frames with information for
all 103 chemicals in the `cvt` dataset that comes with `invivopkfit`.
I will need to do append each dataframe to the last for the outputs of the following
methods:

- `AIC()`
- `BIC()` left-joined with `AIC` output
- `get_tkstats()`

I will also have to fit these iteratively and manage the memory as part of the loop.

@@

@@

ggsave(paste0(Sys.getenv("FIG_DIR"), "Point_Reference_3x5.png"),
       units = "in",
       height = 3,
       width = 5,
       device = "png",
       dpi = 300)

# Notes

Specify that favorable gains in Cmax RMSE not accompanied by gains in AUC RMSE.
Histogram of Volume of Distributions and half-lifes... other TKstats... Lombardo comparison
- Stratified on species... then chemical class (pharma vs non-pharma, Pharmapendium)
- Classyfier for chemical superclass (talk to Paul) Ranges and Mean for each class...

>>>>

Here I evaluate the various fitting options by counting the number of fits 
for each model that "won" based on AIC. This is given by the `get_winning_model`
method. Furthermore, I also calculate the root mean squared error (RMSE)
for AUC~inf~ and C~max~ values. The _observed_ values in this calculation are
the results of the non-compartmental analysis. Importantly,
all Chemical, Species, Reference, Route, Media, Dose data groups with
AUC~inf~ values that are non-finite or zero in either
non-compartmental or _invivoPKfit_ analysis are not included in the 
calculation for RMSE (of AUC or C~max~). This is to exclude the "incalculable"
RMSEs such that they won't impact our assessment of each set of options'
_goodness-of-fit_. Lastly, we calculate more detailed statistics such as R^2^
and average fold error for each model, method, and set **data_group** for downstream
analyses.

```{r Evaluation-helpers}
# Evaluation
# Current:

@@

  return(full_list)
}
gc()
```

```{r Evaluating choices}

@@

These finalists will be compared based on their more detailed statistics.

@@

# What are the sheets names
readxl::excel_sheets(paste(Sys.getenv("OD_DIR"),
                           "DataSummary_9_21_2023.xlsx",
                           sep = "/")) # Predictions Evaluation

@@

Dose-normalization and a hierarchical model were the options that produced the least
amount of error in predictions and derived TK stats.
In addition, _L-BFGS-B_ was the optimizer of choice due to some marginally better fits
(I will note that the run-time for _L-BFGS-B_ is significantly faster).

@@

Next I will generate the figures for the paper.

@@

Here I decide to investigate data where fits were aborted and how many 
time-points occurred before non-compartmental t~max~, which essentially
asks whether there are enough detectable (above LOQ) data points to model absorption.
As a threshold for whether absorption can be modeled, I count those that have at least
more than one data point prior to the empirical t~max~. With at least three points
(including t~max~) we can reasonably begin to assess the absorption of a compound.

@@

Here is the code used to generate the CvT data and _invivoPKfit_ fits
for each chemical, species data group.

@@

ggsave(paste0(Sys.getenv("FIG_DIR"), "Point_Reference_3x5.png"),
       units = "in",
       height = 3,
       width = 5,
       device = "png",
       dpi = 300)
```

# Notes and future directions
- Stratified on species... then chemical class (pharma vs non-pharma, Pharmapendium)
- Classyfier for chemical superclass (talk to Paul) Ranges and Mean for each class...
